Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-04-23 papers/ms.tex
update ms
bug-fix auto cluster viz in fig1, fig2 CAMDs.
still need to propagate to rotation period plots and tables.

\newcommand{\npms}{1{,}097} % 20220311_Kerr_SPYGLASS205_Members_All.csv

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 70] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -3] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [4, 6] \nonumber
\end{align}
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield 141
candidate RSG-5 members, and 37 candidate CH-2 members.
These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by
Kepler.
An important consideration, especially for CH-2, is the
contamination rate by field stars.  We assess this in the following
section.

@@

The CAMDs show that for RSG-5, nearly all of our candidate members are
on a tight pre-main-sequence locus.  This implies a false positive
rate of a few percent, at most.  By comparison, our control sample
(the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk cluster
population.  For CH-2, our membership selection gives 27 objects in
the color range displayed, and 23 of them appear to be consistent with
being on the pre-main-sequence.  This implies a false positive rate in
CH-2 of $\approx$15\%.

@@

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew 141 candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our 37 candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The ratio of number
densities (candidate members per unit searched volume) in RSG-5
relative to CH-2 is 34 to 1.

@@

\paragraph{Table~3} contains spatial, kinematic, astrometric, and rotation period
information for the 141 candidate RSG-5 members and 37 candidate CH-2
members described in Section~\ref{subsec:members}.
These are the data used to make the lower panels of
Figure~\ref{fig:age}.
Table~3 includes rotation periods for 53 stars with ZTF and 51 stars with
 TESS, for a total of 71 periods reported for unique stars and 32
 overlapping between the surveys. We adopted the ZTF period over the
 TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
 Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
 period of 6.61 days; however, we flagged it as a candidate
 double-dipper, which appears to have inaccurately doubled the TESS
 period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
 days with TESS and 6.64 days with ZTF; we suspect that TESS captured
 the 1/2-period harmonic and adopt the approximately double value from
 ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
 with TESS from Cycle 2, but noted that the signal appeared to be
 missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
 adopt this as the star's period. In the remaining overlap cases, we
 adopted the average between TESS and ZTF as the final period. For
 these overlap stars, the median absolute deviation is 0.01 days,
 showing remarkable consistency between the surveys. For three stars,
 we failed to detect a period in TESS but recovered one from ZTF; in
 all cases the periods appear to be 13--16 days.
 These stars were: (1) Gaia EDR3
 2129930258400157440, for which TESS showed a flat light curve while ZTF yielded
 a 15.3-day period; (2) Gaia EDR3 2082376861542398336, LS found a
 7.6-day period which we rejected during visual validation; we found
 15.4 days with ZTF, and we suspect that the weak/rejected signal form
 TESS might have been a 1/2 period harmonic; (3) Gaia EDR3
 2082397099429013120, similar to the previous case, we rejected a
 6.7-day signal from TESS and recovered a 12.8-day period with ZTF.

>>>>

\newcommand{\npms}{1{,}097} % 20220311_Kerr_SPYGLASS205_Members_All.csv
\newcommand{\nchtwo}{37} % CH-2_auto_XYZ_vl_vb_cut.csv
\newcommand{\nrsgfive}{173} % RSG-5_auto_XYZ_vl_vb_cut.csv

@@

%
% Numbers are from RSG-5_auto_XYZ_vl_vb_cut.csv,
% CH-2_auto_XYZ_vl_vb_cut.csv
%
We define two sets of stars in the local vicinity of our objects of
interest.  For candidate RSG-5 members, we require:
\begin{align}
  X/{\rm pc} &\in [45, 75] \nonumber \\
  Y/{\rm pc} &\in [320, 350] \nonumber \\
  Z/{\rm pc} &\in [40, 80] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-4, -2.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [3.5, 6], \nonumber
\end{align}
though the cluster does have a greater
spatial extent toward smaller $X$
(Figure~\ref{fig:XYZvtang}, middle panels).
For the diffuse stars near KOI-7368 and KOI-7913, we require
\begin{align}
  X/{\rm pc} &\in [20, 70] \nonumber \\
  Y/{\rm pc} &\in [230, 270] \nonumber \\
  Z/{\rm pc} &\in [75, 105] \nonumber \\
  v_b/{\rm km\,s^{-1}} &\in [-3.5, -1.5] \nonumber \\
  v_{l^*}/{\rm km\,s^{-1}} &\in [2, 6] \nonumber
\end{align}
and we call this latter set of stars ``CH-2''.  These cuts yield
\nrsgfive\ candidate RSG-5 members, and \nchtwo\ candidate CH-2
members.  These stars are listed in Appendix~\ref{app:members}, as are
the Cep-Her candidates that were observed by Kepler.
An important consideration, especially for CH-2, is the
contamination rate by field stars.  We assess this in the following
section.

@@

The CAMDs show that for RSG-5, practically all of our candidate members are
on a tight pre-main-sequence locus.  This implies a false positive
rate of a few percent, at most.  By comparison, our control sample
(the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population, while being outliers from the bulk cluster
population.  For CH-2, our membership selection gives 27 objects in
the color range displayed, and 23 of them appear to be consistent with
being on the pre-main-sequence.  This implies a false positive rate in
CH-2 of $\approx$15\%.

@@

To quantify the density difference between CH-2 and RSG-5, we can compare the spatial and
velocity volumes searched for each group.
For RSG-5, we drew \nrsgfive\ candidate members from a $30\,{\rm
pc}\times30\,{\rm pc}\times30\,{\rm pc}$ spatial cube, given a $1 {\rm
\mkms} \times 2 {\rm \mkms }$ rectangle in apparent galactic velocity.
For CH-2, our \nchtwo\ candidate members came from a rectangular prism of
dimension $50\,{\rm pc}\times40\,{\rm pc}\times30\,{\rm pc}$, and a
rectangular box of $2 {\rm \mkms} \times 4 {\rm \mkms}$.  If we define
the searched volume in units of ${\rm pc}^3\,{\rm km^2}\,{\rm s^{-2}}$, then
the volume ratio of CH-2 to RSG-5 is 9 to 1.  The ratio of number
densities (candidate members per unit searched volume) in RSG-5
relative to CH-2 is 34 to 1.

@@

\paragraph{Table~3} contains spatial, kinematic, astrometric, and rotation period
information for the \nrsgfive\ candidate RSG-5 members and \nchtwo\ candidate CH-2
members described in Section~\ref{subsec:members}.
These are the data used to make the lower panels of
Figure~\ref{fig:age}.
Table~3 includes rotation periods for 53 stars with ZTF and 51 stars with
 TESS, for a total of 71 periods reported for unique stars and 32
 overlapping between the surveys. We adopted the ZTF period over the
 TESS period in three cases: (1) Gaia EDR3 2081755809272821248: the
 Lomb-Scargle periodogram favored 6.67 days, consistent with the ZTF
 period of 6.61 days; however, we flagged it as a candidate
 double-dipper, which appears to have inaccurately doubled the TESS
 period to 13.34 days; (2) Gaia EDR3 2081737529891330560: we found 3.06
 days with TESS and 6.64 days with ZTF; we suspect that TESS captured
 the 1/2-period harmonic and adopt the approximately double value from
 ZTF; (3) 2134851775526125696: for this star, we measured 1.91 days
 with TESS from Cycle 2, but noted that the signal appeared to be
 missing in Cycle 4; ZTF found a strong signal at 12.23 days and we
 adopt this as the star's period. In the remaining overlap cases, we
 adopted the average between TESS and ZTF as the final period. For
 these overlap stars, the median absolute deviation is 0.01 days,
 showing remarkable consistency between the surveys. For three stars,
 we failed to detect a period in TESS but recovered one from ZTF; in
 all cases the periods appear to be 13--16 days.
 These stars were: (1) Gaia EDR3
 2129930258400157440, for which TESS showed a flat light curve while ZTF yielded
 a 15.3-day period; (2) Gaia EDR3 2082376861542398336, LS found a
 7.6-day period which we rejected during visual validation; we found
 15.4 days with ZTF, and we suspect that the weak/rejected signal form
 TESS might have been a 1/2 period harmonic; (3) Gaia EDR3
 2082397099429013120, similar to the previous case, we rejected a
 6.7-day signal from TESS and recovered a 12.8-day period with ZTF.
